A Handbook for Tenured Track Faculty in Computer Science in the US

### 2024-03-21 faculty.tex
updates

\section{Service to your Professional Community}
\section{Service to the Community}
\section{Service to the Department}
\section{Service to the University}
\section{Serving on NSF Panels}

You should serve on NSF panels.  It is a great way to learn about the grant process: how to distinguish between good and bad proposals and how people review propsoals.
It is also a good way learn what other people are doing, what is hot, and what is not. In short, it is a good way to learn how to write successful proposals.

\paragraph{How to get on an NSF panel} You can cold email progarm managers in your area and ask to be on a panel.  You can also ask your colleagues to make recommend for you. Same way you do for getting invited to be on a PC.

\paragraph{How much work is it?} It is a lot of work.  You will be asked to review a dozen proposals in a month or so.  It will be similar to a program committee meeting, where all the proposals will be discussed.  You will be expected to share your view of the paper, and argue for why it should be funded or not.

>>>>

\section{Service to your Professional Community}

These are services that you do for your professional community. They will help you to get to know people in your field, and to get your name out.  Common examples include serving on the program committees of conferences, serving on editorial boards of journal, reviewing papers for journals, serving on grant panels.

\paragraph{Serving on Program Committees (PC)} This is a good way to get to know what is hot in your field, and to get to know people in your field.  It is also a good way to get your name out.
You should try to serve on the program committee of the top conferences in your field.

\textbf{Advice}: You can ask senior colleagues or even your PhD advisor/collaborators to recommend you to serve on a PC. You can also directly email the PC chairs and ask to serve on the PC.  For example, I directly email OOPSLA and PLDI PC chairs and asked to serve on the PC, and they accepted my request (I do have papers at OOPSLA and PLDI when I asked). I tried this with SE conferences  e.g., ICSE (and of course also nominate myself through the official form), and it never work, even though I have many papers at ICSE.

\section{Serving on NSF Panels} You should serve on NSF panels.  It is a great way to learn about the grant process: how to distinguish between good and bad proposals and how people review propsoals.
It is also a good way learn what other people are doing, what is hot, and what is not. In short, it is a good way to learn how to write successful proposals.

Just like serving on a PC, you will review proposals and you will have to argue for why a proposal should be funded or not.  Unlike PC where discussions can spread over many days (and there are also rebuttals), NSF panels are usually a two-day event.  You do get paid a bit for serving on NSF panels and you get to travel to NSF headquarters in Virginia (except during the pandemic where everything is remote).

In general, I enjoy serving on NSF panels much more than serving on PC. While the work is more intense and takes more time, I found it to be more rewarding and learned a lot from it. Since my first NSF panel in 2019, I have served 7 panels (at least once every year since '19) and I look forward to serving more.

\textbf{Advice}: Similarly to serving in PC, you can cold email progarm managers in your area and ask to be on a panel. Once you have served, you will likly be invited to serve again.  Unfortunately, I do not have much experience with non-NSF panels or proposals.

\section{Service to the Department}
\section{Service to the University}
\section{Other Types of Services}
\paragraph{Writing Recommendation Letters} You will be asked to write a lot of recommendation letters, for both students and colleagues.

\textbf{Advice}: you should have a template for recommendation letters.  You can find many templates online.  You should also ask your colleagues to share their templates with you.  You should also ask your colleagues to share their recommendation letters with you.  You can learn a lot from reading other people's recommendation letters.
